---
title: "Assingment_1"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading Libraries
```{r,warning=FALSE}
library(tidyverse)
library(readxl)

platelet <- read_excel("Dataset 2.xlsx")
platelet<- as.data.frame(platelet)
```

#Change necessary columns to factor
```{r,warning=FALSE}
col_names <- names(platelet)
for (i in col_names) {
  if(length(unique(platelet[,i])) <= 4)
  {
    platelet[,i] <- as.factor(platelet[,i])
  }
}
names(platelet)[2]<-"Study_Group"
```

#Binning
```{r,warning=FALSE}
#Binning Continuos Columns
for (col in 3:ncol(platelet)) {
  column = platelet[,col]
 if(is.numeric(column))
  {
  range=(max(column,na.rm = T)-min(column,na.rm = T))/5
    range=round(range)
    min_val<-min(column,na.rm = T)-range
    max_val=max(column,na.rm = T)
    bin=seq(from=min_val,to=max_val,by=range)
    temp <- cut(column,bin)
    
    platelet<-cbind(platelet,temp)
    names(platelet)[match("temp",names(platelet))]<-paste0(names(platelet)[col],"_bins") 
    }
}

```

#Questions:-
##Question 1	Construct frequency distribution of all variables according to Group 1 and Group 2

```{r,warning=FALSE}
freq_dist<- function(clm_to_dist)
{
  dataset <- platelet
  m <<- m+1
  freq_db <- data.frame(cat="a",group="b")
  num_col<-ncol(dataset)
  if(is.numeric(clm_to_dist))
  {
    
    range=(max(clm_to_dist,na.rm = T)-min(clm_to_dist,na.rm = T))/5
    range=round(range)
    min_val<-min(clm_to_dist,na.rm = T)-range
    max_val=max(clm_to_dist,na.rm = T)
    bin=seq(from=min_val,to=max_val,by=range)
    dataset[,num_col+1] <- cut(clm_to_dist,bin)

     t= dataset %>% group_by(dataset[,(num_col+1)]) %>% summarise(Group_1=sum(Study_Group=="Group 1"),Group_2=sum(Study_Group=="Group 2"))
    names(t)[1] =  names(dataset)[m-1]
   
    }
  else if(is.factor(clm_to_dist))
   {
     fac_col<-names(dataset)[m-1]
     t = dataset %>% group_by(dataset[,c(fac_col)]) %>% summarise(Group_1 = sum(Study_Group=="Group 1"),Group_2=sum(Study_Group=="Group 2"))
      names(t)[1] <- fac_col
     }
  
  return(t)
}

m=1
a<-lapply(platelet,freq_dist)
a
View(platelet)

```
##Question 2	Represent the all the given variables below using appropriate graphical presentation
###Numerical Column
```{r,warning=FALSE}
num = sapply(platelet, is.numeric)

plot_graph_num = function(col){
  new = data.frame(col = platelet[,col])
  print(new %>% na.omit() %>% 
            ggplot(aes(x=col)) + geom_histogram(fill = 'steelblue',bins = 10) + xlab(col))
}

sapply(names(platelet)[num], plot_graph_num)
```
###Categorical Column
```{r,warning=FALSE}
num = sapply(platelet, is.numeric)

gen_plot = function(col){
  new = data.frame(col = platelet[,col])
  print(new %>% na.omit() %>% 
            ggplot(aes(x=col)) + geom_bar(fill = 'steelblue') + xlab(col))
}

sapply(names(platelet)[!num], gen_plot)
```

##Question 3	Construct the cross tables of Age versus Sex, Culture 1 and Culture 2
```{r,warning=FALSE}
cross_tab <- function(versus=c("Sex","Culture 1","Culture 2"))
{
   cross_tab_list=list()
  for (col in versus) {
    cross_tab_list[[col]]=table(platelet[,"Age (yrs)_bins"],platelet[,col])
  }
  return(cross_tab_list)
}


cross_tab()
```

##Question 4	Compute the mean and standard deviation of data obtained in the age frequency distribution 
```{r,warning=FALSE}
freq_dist_age <- platelet %>% group_by(`Age (yrs)_bins`) %>% summarise(Total_occurence=n())
mid_vector=c()
for (row in 1:6) {
  bined_age<-freq_dist_age$`Age (yrs)_bins`[row]
 trimed_range<-gsub("\\(|\\]","",bined_age)
 num_min_max<-as.numeric(unlist(strsplit(trimed_range,",")))
 mid = (num_min_max[2]-num_min_max[1])/2
 mid_vector <- append(mid_vector,(mid+num_min_max[1]))  
}
freq_dist_age<-cbind(freq_dist_age,mid_vector)

freq_dist_age<-freq_dist_age %>% mutate(F.X=Total_occurence*mid_vector)
mean_Age_Freq_Distribution<-sum(freq_dist_age$F.X)/sum(freq_dist_age$Total_occurence)

SD_Age_Freq_Didtribution <- sqrt(sum(((freq_dist_age$mid_vector-mean_Age_Freq_Distribution)^2)*freq_dist_age$Total_occurence))/sqrt(sum(freq_dist_age$Total_occurence))

mean_Age_Freq_Distribution

SD_Age_Freq_Didtribution
```
##Question 5	Construct the cross tables between Culture 1 and Culture 2
```{r}
cross_tab<- platelet %>% group_by(`Culture 1`) %>% summarise(Culture2_Negative=sum(`Culture 2`=="Negative"),Culture2_positive=sum(`Culture 2`=="Positive"))
cross_tab
```

##Question 6	Present the summary statistics of all quantitative variables
```{r,warning=FALSE}
num_col <- sapply(platelet, is.numeric)
sum_list<- lapply(platelet[,num_col], function(x){if(is.numeric(x)){summary(x)}else{return()}})
sum_list
```

##Question 7	Draw a scattered diagram between Systolic blood pressure and Diastolic blood pressure
```{r,warning=FALSE}

ggplot(platelet,aes(x=`Systolic blood presure`,y=`Diastolic blood presure`))+geom_point() +ggtitle("Systolic blood presure VS Diastolic blood presure")

```
##Question 8	Present all the quantitative data using box-and Whisker plot 

```{r,warning=FALSE}
num_col <- sapply(platelet, is.numeric)

n=0
plot1 <- function(col) {
  n<<-n+1
  if(is.numeric(col))
  {
    col_name <- names(platelet)[n]
     ggplot(platelet,aes(x=col_name,y=col)) + geom_boxplot() +ggtitle(paste0(col_name," BOX AND WISKER PLOT"," "))
  }
}
a<-sapply(platelet, plot1)
b<-sapply(a, function(x){!is.null(x)})
a[b]
```

